Price of Anarchy for Mean Field Games

### 2018-07-13 PoA_response_to_referee.tex

\documentclass[]{article}

%opening
\title{Response to Referee}
\author{}

\begin{document}

\maketitle

We would like to thank the reviewer for their remarks. We have addressed each of their points as follows:

Main Points:
\begin{enumerate}
	\item 
\end{enumerate}

Minor Points:
\begin{enumerate}
	\item 
\end{enumerate}

In addition to the suggested revisions, we have also made the following minor modifications:
\begin{enumerate}
	\item 
\end{enumerate}

\end{document}

### 2018-07-14 PoA.tex
editing proposition 3

As in the previous section, this is a linear FBSDE of McKean-Vlasov type, which can be solved explicitly under mild assumptions (or at least in the case of time-independent coefficients which we will consider later. See Appendix \ref{appendix_solving_fbsdes}). Let $\bar{\eta}_t^{MKV}$, $\eta_t^{MKV}$, $\bar{x}_t^{MKV}$, and $v^{MKV}_t$ so that $Y_t=\eta_t^{MKV}X_t+(\bar{\eta}_t^{MKV}-\eta_t^{MKV})\bar{x}_t^{MKV}$, $\mathbb{E}(Y_t)=\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}$, $\mathbb{E}(X_t)=\bar{x}_t^{MKV}$, and $Var(X_t)=v^{MKV}_t$ provide a solution to the LQEMKV problem. Then from the appendix, we have:
\begin{equation}
\begin{split}
\dot{\bar{\eta}}^{MKV}_t+c^{MKV}(t)(b_2(t)+\bar{b}_2(t)) (\bar{\eta}^{MKV}_t)^2+2(b_1(t)+\bar{b}_1(t)) \bar{\eta}^{MKV}_t +q(t)+\bar{q}(t)(1-s(t))^2&=0,\\
\bar{\eta}^{MKV}_T-(q_T+\bar{q}_T(1-s_T)^2)&=0,
\end{split}
\label{eq:eta_bar_MKV}
\end{equation}
\begin{equation}
\begin{split}
\dot{\eta}^{MKV}_t+a^{MKV}(t)b_2(t)(\eta^{MKV}_t)^2+2b_1(t)\eta^{MKV}_t+q(t)+\bar{q}(t)&=0, \\
\eta^{MKV}_T-(q_T+\bar{q}_T)&=0,
\end{split}
\end{equation}
\begin{equation}
\begin{split}
\dot{\bar{x}}^{MKV}_t&=(b_1(t)+\bar{b}_1(t)+c^{MKV}(t)(b_2(t)+\bar{b}_2(t))\bar{\eta}^{MKV}_t)\bar{x}^{MKV}_t, \\
\bar{x}^{MKV}_0&=\mathbb{E}(\xi).
\end{split}
\label{eq:x_bar_MKV}
\end{equation}
And thus,
\begin{equation*}
\bar{x}^{MKV}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1(u)+\bar{b}_1(u)+c^{MKV}(u)(b_2(u)+\bar{b}_2(u)\bar{\eta}^{MKV}_u)du},
\end{equation*}
\begin{equation*}
v^{MKV}_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MKV}(s)b_2(s)\eta^{MKV}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MKV}(u)b_2(u)\eta^{MKV}_u) du}ds.
\end{equation*}
Then $SC^{MKV}=SC(\phi)$ where $\phi$ is the feedback function specified by this solution, i.e.
\begin{equation*}
    \phi(t,x)=a^{MKV}(t)\eta_t^{MKV}x+\left(a^{MKV}(t)(\bar{\eta}_t^{MKV}-\eta_t^{MKV})+b^{MKV}(t)\bar{\eta}_t^{MKV} \right)\bar{x}_t^{MKV}.
\end{equation*}
Then we can compute the social cost, denoted $SC^{MKV}$, as described in Section \ref{sub:MKV_formulation}:
\begin{equation*}
\begin{split}
    SC^{MKV}=&\frac{1}{2}[(q_T+\bar{q}_T)v_T^{MKV}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MKV})^2\\
    &+\int_0^T (q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MKV}(t)\eta_t^{MKV})^2)v_t^{MKV}dt \\
    &+\int_0^T(q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MKV}(t)\bar{\eta}_t^{MKV})^2)(\bar{x}_t^{MKV})^2dt],
\end{split}
\end{equation*}
where we have used the fact that:
\begin{equation*}
    \mathbb{E}(\phi(t,X_t))=c^{MKV}(t)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV},
\end{equation*}
and:
\begin{equation*}
    Var(\phi(t,X_t))=(a^{MKV}(t)\eta_t^{MKV})^2v^{MKV}_t.
\end{equation*}

@@

\begin{corollary}
    Assuming (\ref{eq:assumptions}), if the initial condition $\xi$ is such that $\mathbb{E}(\xi)=0$, then $PoA=1$.
\end{corollary}
\begin{proof}
    By equation (\ref{eq:x_bar_MFG_explicit}), $\mathbb{E}(\xi)=0$ implies $\bar{x}^{MFG}_t=0,\ \forall t \in [0,T]$. Therefore by Proposition \ref{prop:diff_SC}, $\Delta SC=0$. From equation (\ref{eq:v_t}), $v_t>0$ which implies $h_{var}>0$. Therefore by equation (\ref{eq:SC_MKV_2}), $SC^{MKV}>0$. We conclude that $PoA=1$.
\end{proof}

@@

% proposition r infinity
\begin{proposition}
	Assuming (\ref{eq:assumptions}),
	\begin{equation*}
			\lim_{r \to \infty} PoA = 1 \qquad \text{and} \qquad
			\lim_{\bar{r} \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:r_bar_r}
\end{proposition}
\begin{proof}
	When assumption $(\ref{eq:assumptions})$ is satisfied, we have the existence and uniqueness of solutions to the scalar Riccati equations associated with $u^{r}_t$, $w^{r}_t$ and $\eta^{r}_t$ for every given $r >0$. The superscript $r$ here indicates the dependence on this coefficient because we intend to study the behavior of these solutions in the asymptotic regime.

	When $r \to \infty$, we have
	\begin{equation*}
		\lambda^r \longrightarrow \lambda^{r\to\infty} := \frac{b_2}{b_2 + \bar{b}_2}
	\end{equation*}
	and
	\begin{equation*}
	\begin{array}{l}
		B^r \longrightarrow 0,\quad \ B^{\eta,r} \longrightarrow 0,\\
		C^{u,r} \longrightarrow C_u^{r\to \infty} := \lambda^{r \to \infty}(q + \bar{q}(1-s)),\quad \ D^{u,r} \to D_u^{r \to \infty} := \lambda^{r \to \infty}(q_T+ \bar{q}_T(1-s_T)).
	\end{array}
	\end{equation*}

	In order to show that the $PoA$ tends to $1$, we can indeed show that $\Delta SC^{r}$ tends towards $0$ while $SC^{r, MKV} >0$ in the asymptotic regime. From the equation (\ref{eq:PoA_LQ}), a sufficient condition is to demonstrate that $\int_0^T (u^r_t - w^r_t)^2 (\bar{x}_t^{r,MFG} )^2 dt$ is finite and the variance function $v^r_t$ is strictly positive in the asymptotic regime.\\

	% modification Main point 5 (nicolas)
	If $A^u \neq 0$, let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the first-order differential equation:
	\begin{equation}
		\dot{\left({u}^{r \to \infty}_t\right)} - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u,
	\end{equation}
	or if $A^u = 0$, let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ solve:
	\begin{equation}
		\dot{\left(u^{r\to \infty}_t\right)} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
	\end{equation}	
	Since assumption (\ref{eq:assumptions}) holds for arbitrarily large $r$, from the explicit formula of the solution to the scalar Riccati equation (see Appendix \ref{appendix_solving_fbsdes} equation (\ref{eq:riccati_ut_sol_app})), it is easy to show that the solution $u^r$ to equation (\ref{eq:riccati_ut}) converges pointwise for every time $t\in [0,T]$ to the solution $u^{r \to \infty}$ as long as $r \to \infty$. This limiting solution $u^{r \to \infty}$ can be given by the following expressions: for every $t\in [0,T]$
	\begin{equation*}
	\begin{split}
	    \text{when } A^u \neq 0,\qquad & u_t^{r \to \infty} = \left(D^{r \to \infty}_u - \frac{C^{r \to \infty}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{r \to \infty}_u}{2A^u},\\
	    \text{when } A^u = 0, \qquad & u_t^{r \to \infty} = D^{r \to \infty}_u + C^{r \to \infty}_u (T-t).
	\end{split}
	\end{equation*}

@@

	Since $B^{\eta} \to 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, we get:
	\begin{equation*}
	\begin{split}
	    \text{when } A^\eta \neq 0, \qquad & \eta_t \to \eta^{0,b_2}_t := \left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} },\\
	    \text{when } A^{\eta} = 0, \qquad & \eta_t \to \eta^{0,b_2}_t := D^{\eta} - C^{\eta}(T-t),
	\end{split}
	\end{equation*}
	which are bounded over $[0,T]$. Thus, the variance function $ v_t $ converges to some positive bounded function $ v^{0,b_2}_t := Var(\xi)e^{2b_1t}+ \sigma^2 \int_0^t e^{2b_1(t-s)}ds>0$ for every given time $t\in [0,T]$.
	Using the fact that $w^{0,b_2}_t\not \equiv 0$  and together with the equation (\ref{eq:SC_MKV_2}), we have $0< \lim_{b_2\to 0} SC^{MKV} <\infty $ .

@@

	Now we consider the case when $b_2 \to \infty$. It can be seen later in the proof that both $SC^{MFG}$ and $SC^{MKV}$ tend towards $0$. In order to study the limit of the PoA,  the idea becomes to estimate the order of magnitude in terms of $b_2$ for the quantity $\Delta SC$ and $SC^{MKV}$.

>>>>

As in the previous section, this is a linear FBSDE of McKean-Vlasov type, which can be solved explicitly under mild assumptions (or at least in the case of time-independent coefficients which we will consider later. See Appendix \ref{appendix_solving_fbsdes}). Let $\bar{\eta}_t^{MKV}$, $\eta_t^{MKV}$, $\bar{x}_t^{MKV}$, and $v^{MKV}_t$ so that $Y_t=\eta_t^{MKV}X_t+(\bar{\eta}_t^{MKV}-\eta_t^{MKV})\bar{x}_t^{MKV}$, $\mathbb{E}(Y_t)=\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}$, $\mathbb{E}(X_t)=\bar{x}_t^{MKV}$, and $Var(X_t)=v^{MKV}_t$ provide a solution to the LQEMKV problem. Then from the appendix, we have:
\begin{equation}
\begin{split}
\dot{\bar{\eta}}^{MKV}_t+c^{MKV}(t)(b_2(t)+\bar{b}_2(t)) (\bar{\eta}^{MKV}_t)^2+2(b_1(t)+\bar{b}_1(t)) \bar{\eta}^{MKV}_t +q(t)+\bar{q}(t)(1-s(t))^2&=0,\\
\bar{\eta}^{MKV}_T-(q_T+\bar{q}_T(1-s_T)^2)&=0,
\end{split}
\label{eq:eta_bar_MKV}
\end{equation}
\begin{equation}
\begin{split}
\dot{\eta}^{MKV}_t+a^{MKV}(t)b_2(t)(\eta^{MKV}_t)^2+2b_1(t)\eta^{MKV}_t+q(t)+\bar{q}(t)&=0, \\
\eta^{MKV}_T-(q_T+\bar{q}_T)&=0,
\end{split}
\end{equation}
\begin{equation}
\begin{split}
\dot{\bar{x}}^{MKV}_t&=(b_1(t)+\bar{b}_1(t)+c^{MKV}(t)(b_2(t)+\bar{b}_2(t))\bar{\eta}^{MKV}_t)\bar{x}^{MKV}_t, \\
\bar{x}^{MKV}_0&=\mathbb{E}(\xi).
\end{split}
\label{eq:x_bar_MKV}
\end{equation}
And thus,
\begin{equation}
\bar{x}^{MKV}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1(u)+\bar{b}_1(u)+c^{MKV}(u)(b_2(u)+\bar{b}_2(u)\bar{\eta}^{MKV}_u)du},
\label{eq:x_bar_MKV}
\end{equation}
\begin{equation}
v^{MKV}_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MKV}(s)b_2(s)\eta^{MKV}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MKV}(u)b_2(u)\eta^{MKV}_u) du}ds.
\label{eq:v_t_MKV}
\end{equation}
Then $SC^{MKV}=SC(\phi)$ where $\phi$ is the feedback function specified by this solution, i.e.
\begin{equation*}
    \phi(t,x)=a^{MKV}(t)\eta_t^{MKV}x+\left(a^{MKV}(t)(\bar{\eta}_t^{MKV}-\eta_t^{MKV})+b^{MKV}(t)\bar{\eta}_t^{MKV} \right)\bar{x}_t^{MKV}.
\end{equation*}
Then we can compute the social cost, denoted $SC^{MKV}$, as described in Section \ref{sub:MKV_formulation}:
\begin{equation*}
\begin{split}
    SC^{MKV}=&\frac{1}{2}[(q_T+\bar{q}_T)v_T^{MKV}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MKV})^2\\
    &+\int_0^T (q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MKV}(t)\eta_t^{MKV})^2)v_t^{MKV}dt \\
    &+\int_0^T(q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MKV}(t)\bar{\eta}_t^{MKV})^2)(\bar{x}_t^{MKV})^2dt],
\end{split}
\end{equation*}
where we have used the fact that:
\begin{equation*}
    \mathbb{E}(\phi(t,X_t))=c^{MKV}(t)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV},
\end{equation*}
and:
\begin{equation*}
    Var(\phi(t,X_t))=(a^{MKV}(t)\eta_t^{MKV})^2v^{MKV}_t.
\end{equation*}

@@

\begin{corollary}
    Assuming (\ref{eq:assumptions}), if the initial condition $\xi$ is such that $\mathbb{E}(\xi)=0$, then $PoA=1$.
\end{corollary}
\begin{proof}
    By equation (\ref{eq:x_bar_MFG_explicit}), $\mathbb{E}(\xi)=0$ implies $\bar{x}^{MFG}_t=0,\ \forall t \in [0,T]$. Therefore by Proposition \ref{prop:diff_SC}, $\Delta SC=0$. From equation (\ref{eq:v_t}), which we recall is equivalent to equation (\ref{eq:v_t_MKV}), $v_t>0$ which implies $h_{var}>0$. Therefore by equation (\ref{eq:SC_MKV_2}), $SC^{MKV}>0$. We conclude that $PoA=1$.
\end{proof}

@@

To make the following computations easier to follow, we repeat equations (\ref{eq:PoA_LQ}), (\ref{eq:x_bar_MFG_explicit}), and (\ref{eq:v_t}), which we recall is equivalent to  equation (\ref{eq:v_t_MKV}), using the above notations:
\begin{equation}
PoA =1+ \frac{\Delta SC}{SC^{MKV}}= 1 +  \frac{ \displaystyle   \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}  \int_0^T (u_t-w_t)^2 \cdot (\bar{x}_t^{MFG})^2 dt }{\displaystyle \int_0^T \left[q+\bar{q} + \frac{b_2^2}{r+\bar{r}} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T + w_0 (\mathbb{E}(\xi))^2}.
\label{eq:PoA_LQ_new_notation}
\end{equation}
\begin{equation}
\bar{x}^{MFG}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1+\bar{b}_1-Bu_s)ds},
\label{eq:x_bar_MFG_explicit_new_notation}
\end{equation}
\begin{equation}
v_t=Var(\xi)e^{\int_0^t 2(b_1-B^{\eta} \eta_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1-B^{\eta}\eta_u) du}ds.
\label{eq:v_t_new_notation}
\end{equation}

% proposition r infinity
\begin{proposition}
	Assuming (\ref{eq:assumptions}),
	\begin{equation*}
			\lim_{r \to \infty} PoA = 1 \qquad \text{and} \qquad
			\lim_{\bar{r} \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:r_bar_r}
\end{proposition}
\begin{proof}
	First, we consider $r \to \infty$. When assumption $(\ref{eq:assumptions})$ is satisfied, for every given $r >0$, we have existence and uniqueness of the solutions $u^{r}_t$, $w^{r}_t$ and $\eta^{r}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that we have added the superscript $r$ to emphasize the dependence on this coefficient.

	When $r \to \infty$, we have:
	\begin{equation*}
		\lambda^r \longrightarrow \lambda^{r\to\infty} := \frac{b_2}{b_2 + \bar{b}_2},
	\end{equation*}
	and
	\begin{equation*}
	\begin{array}{l}
		B^r \longrightarrow 0,\quad \ B^{\eta,r} \longrightarrow 0,\\
		C^{u,r} \longrightarrow C_u^{r\to \infty} := \lambda^{r \to \infty}(q + \bar{q}(1-s)),\quad \ D^{u,r} \to D_u^{r \to \infty} := \lambda^{r \to \infty}(q_T+ \bar{q}_T(1-s_T)).
	\end{array}
	\end{equation*}

	In order to show that $\lim_{r \to \infty} PoA^r = 1$, it suffices to show that $\lim_{r \to \infty}\Delta SC^{r} = 0$ while $\lim_{r \to \infty} SC^{r, MKV} >0$. From equation (\ref{eq:PoA_LQ_new_notation}), a sufficient condition is to demonstrate that $\lim_{r \to \infty}\int_0^T (u^r_t - w^r_t)^2 (\bar{x}_t^{r,MFG} )^2 dt<\infty$, $\lim_{r \to \infty}v^r_T>0$, and $\lim_{r \to \infty}w^r_0>0$.\\

	% modification Main point 5 (nicolas)
	Let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the first-order differential equation:
	\begin{equation}
		\dot{\left({u}^{r \to \infty}_t\right)} - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
	\end{equation}
	Then we have:
	\begin{equation*}
	\begin{split}
	\text{when } A^u \neq 0,\qquad & u_t^{r \to \infty} = \left(D^{r \to \infty}_u - \frac{C^{r \to \infty}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{r \to \infty}_u}{2A^u},\\
	\text{when } A^u = 0, \qquad & u_t^{r \to \infty} = D^{r \to \infty}_u + C^{r \to \infty}_u (T-t).
	\end{split}
	\end{equation*}
	It is easy to show that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$.

@@

	Since $B^{\eta} \to 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, we get:
	\begin{equation*}
	\begin{split}
	    \text{when } A^\eta \neq 0, \qquad & \eta_t \to \eta^{0,b_2}_t := \left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} },\\
	    \text{when } A^{\eta} = 0, \qquad & \eta_t \to \eta^{0,b_2}_t := D^{\eta} - C^{\eta}(T-t),
	\end{split}
	\end{equation*}
	which are bounded over $[0,T]$. Thus, the variance function $ v_t $ converges to some positive bounded function $ v^{0,b_2}_t := Var(\xi)e^{2b_1t}+ \sigma^2 \int_0^t e^{2b_1(t-s)}ds>0$ for every given time $t\in [0,T]$.
	Using the fact that $w^{0,b_2}_t\not \equiv 0$  and together with equation (\ref{eq:SC_MKV_2}), we have $0< \lim_{b_2\to 0} SC^{MKV} <\infty $ .

@@

	Now we consider the case when $b_2 \to \infty$. It can be seen later in the proof that both $SC^{MFG}$ and $SC^{MKV}$ tend towards $0$. In order to study the limit of $PoA$,  the idea becomes to estimate the order of magnitude in terms of $b_2$ for the quantity $\Delta SC$ and $SC^{MKV}$.
